The SMT Competition 2015--2018

### 2019-04-13 2018/report/SMT-COMP.tex
TODO 16: add brief explanation of competition-wide ranking

In 2014, the SMT Competition was part of the FLoC Olympic Games.
These gave the competition increased visibility and sponsored three
Kurt G\"odel medals.  After substantial internal debate, the 2014
competition organizers decided to award these to the winner of the
Main track's QF\_BV division (which had historically been the logic
with the largest number of solver submissions and job pairs), as well
as to the two best Main-track solvers according to a competition-wide
ranking that had been instituted especially for this
purpose~\cite{CDW14}.  This ranking emphasizes breadth of solver
participation---a solver participating in many logics does not need to be the
best in any one of them to rank highly.

>>>>

In 2014, the SMT Competition was part of the FLoC Olympic Games, which
sponsored three Kurt G\"odel medals.  These were awarded to the winner
of the Main track's QF\_BV division (which had historically been the
logic with the largest number of solver submissions and job pairs), as
well as to the two best Main-track solvers according to a
competition-wide ranking that had been instituted especially for this
purpose~\cite{CDW14}.  This ranking combines each solver's performance
across all competitive Main-track divisions into a single score,
giving more weight to larger divisions, and to solvers that solve a
large fraction of the benchmarks~\cite{rules18}.  It emphasizes
breadth of solver participation---a solver participating in many
logics does not need to be the best in any one of them to rank highly.
